### 2024-07-26 Data/AnalysisData/codebook_item_number_change_data.Rmd
added supplementary analyses regarding the influence of number of items modification, and checked some data loading and storing.

---
title: "Codebook created on 2024-05-22 at 2024-05-22 10:01:49.511004"
output: github_document
---

@@

## Dataset description
The data contains 112 cases and 91 variables.

@@

```{r}
summaries <- read.csv("codebook_plot_data_structure_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

>>>>

---
title: "Codebook created on 2024-07-26 at 2024-07-26 14:09:18.516523"
output: github_document
---

@@

## Dataset description
The data contains 12 cases and 6 variables.

@@

```{r}
summaries <- read.csv("codebook_item_number_change_data.csv", stringsAsFactors = FALSE)
summaries <- summaries[, !colSums(is.na(summaries)) == nrow(summaries)]
options(knitr.kable.NA = '')
knitr::kable(summaries, row.names = FALSE, digits = 2)
```

### 2024-07-26 Data/AnalysisData/codebook_plot_456_data.Rmd
added supplementary analyses regarding the influence of number of items modification, and checked some data loading and storing.

---
title: "Codebook created on 2024-02-27 at 2024-02-27 16:22:04.046895"
output: github_document
---

@@

## Dataset description
The data contains 924 cases and 4 variables.

>>>>

---
title: "Codebook created on 2024-07-26 at 2024-07-26 14:28:36.553505"
output: github_document
---

@@

## Dataset description
The data contains 924 cases and 6 variables.

### 2024-07-26 Data/Data_package_description.Rmd
added supplementary analyses regarding the influence of number of items modification, and checked some data loading and storing.

>>>>

### item_number_change_data.csv

*Explanation:* Contains the many_labs_version, rep_org, title, and mod_5_rev variablefrom the coded_data_replication.csv dataset of the observations where the mod_5_rev variable was TRUE (meaning that the measure's number of items and/or number of response options was modified from original to replication. Additionally, two variables were added to determine whether for that measure the number of items were decreased from original to replication.

-   **context:** A description of the change in item numbers from original to replication. NA means that for that measure the number of items was not changed.

-   **direction:** A factor indicating whether the number of items was decreased, increased, or no change (NA) from original to replication.

### 2024-07-26 Scripts/Manuscript/manuscript.Rmd
added supplementary analyses regarding the influence of number of items modification, and checked some data loading and storing.

```{r FinalPreparationData, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run!
### this code prepares the various pieces of data to be ready to use for the 
### analyses.
## confirmatory analyses
# for hypothesis 4
data_h4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
# for hypothesis 5
data_h5 <- data_prep_H5(coded_data_replications)
# for hypothesis 6
data_h6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)

# for hypothesis 1
data_h1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
# for hypothesis 2
data_h2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean, data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
# for hypothesis 3
data_h3_multiple <- Data_prep_H3_multiple(data_h5, data_h2)
data_h3_avg <- Data_prep_H3_avg(data_h5, data_h3_multiple)

@@

Our data had a multilevel structure. Each replication was nested within one of four Many Labs projects. Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^1]. Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication. In the replications, the data of responses on the measures was further nested in several labs per replication. The combined sample size of all labs in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.

```{r InformationOnMeasurementModification}
# Here we determine whether items had the number of items changed, and how.

# The code below indexes the scales for which either the number of items or 
# number of response options were decreased.

item_number_change_data <- coded_data_replications[!is.na(coded_data_replications$mod_5_REV) & coded_data_replications$mod_5_REV, c(1, 2, 3, 56)]

# Extracted information on the modification of measurement items. When NA is 
# reported it means that we found no modification of number of items.
item_number_change_data$context <- c("from 3 questions about 15 topics -> 1 question about four topics", NA, "from a list of quotations to only the 1 of interest", "From four IATs to 1 IAT in replications", "Initial study used 6 items from an 8-item short scale, 25-item four factor scale suggested by original authors, but 5-item subscale of specific factor of interest", NA,  "Original research had 19 scenarios, replication participants got randomly assigned to 1 control and 3 moral dilemmas from the set of 19", " from a 10-item scale, to single-item scale.", NA, NA, "Compared to the 'longer lists of anagrams used' in previous research (226 for 4 dimensions) on the topic, they switched to a shorter 4 anagram task of the 1 dimension of interest.", "Original measure assessed 4 constructs with 24 item, For the replication they switched to a different scale measuring the 1 construct relevant to the effect using 7 items.")

# Whether the change was a decrease or increase in items
item_number_change_data$direction <- as.factor(c("decrease", NA, "decrease", "decrease", "decrease", NA, "decrease", "decrease", NA, NA, "decrease", "increase"))

# sum(item_number_change_data$direction == "decrease", na.rm = TRUE)

# creating indexes for decreasing items to see if there are noteworthy differences.
decreased_items_index <- rep(FALSE, nrow(coded_data_replications))

# setting to true in case items were decreased.
decreased_items_index[as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),]))] <- TRUE

# getting information on hypothesis support
hypothesis_support_index <- coded_data_replications$hypothesis_support

hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "Yes"

# coding Unclear into No instead of Yes didn't make a difference on the test.
# hypothesis_support_index[coded_data_replications$hypothesis_support == "Unclear"] <- "No"

# chi-squared test of differences in hypothesis support between measures for 
# which items were decreased and for which it was not.
chisq.test(decreased_items_index, coded_data_replications$hypothesis_support)

# Interestingly, when item numbers were decreased, the replicability seemed to have increased in this scenario.
# Although the difference was not significant and there were too few modifications to the items to get a stable estimate.

#mean(coded_data_replications$hypothesis_support[!as.numeric(rownames(coded_data_replications)) %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),]))] == "Yes")

### Looking at the relevancy for Hypothesis tests.
# H1
coded_data_original_shortened$reliability_type[decreased_items_index]
coded_data_replications$reliability_type[decreased_items_index]

# Only one of these measures had a reported reliability in the original, so it
# is unlikely to have been of much impact.

# H2
coded_data_original_shortened$reliability_coeff[decreased_items_index]
coded_data_replications$reliability_coeff[decreased_items_index]

data_h3_avg[data_h3_avg$reporting_index %in% as.numeric(rownames(item_number_change_data[item_number_change_data$direction == "decrease" & !is.na(item_number_change_data$direction),])),]

# Of the measures we could calculate the reliability of, only the measure of 
# persistence was decreased in item count. This was interestingly the one with
# the lowest calculated average alpha in the sample.

@@

@@

We used logistic regression to test the association between the QMP ratio in replication protocols and replication success. In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`). However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^2].

[^2]: As of writing this article the *betareg* package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the *betareg* package) to fit the Gaussian model.

>>>>

```{r FinalPreparationData, include = FALSE, eval = FALSE}
##### Data already available, code does not need to be run
### this code prepares the various pieces of data to be ready to use for the 
### analyses.
## confirmatory analyses
# for hypothesis 4
data_h4 <- data_prep_H4(coded_data_original_shortened, coded_data_replications)
# for hypothesis 5
data_h5 <- data_prep_H5(coded_data_replications)
# for hypothesis 6
data_h6 <- data_prep_H6(coded_data_original_shortened, coded_data_replications)

# for hypothesis 1
data_h1 <- data_prep_H1(coded_data_original_shortened, coded_data_replications)
# for hypothesis 2
data_h2 <- data_prep_H2(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean, data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)
# for hypothesis 3
data_h3_multiple <- Data_prep_H3_multiple(coded_data_replications, data_h2)
data_h3_avg <- Data_prep_H3_avg(coded_data_replications, data_h3_multiple)

@@

Our data had a multilevel structure. Each replication was nested within one of four Many Labs projects. Furthermore, `r sum(coded_data_replications$appearance != 1)` replications used more than one primary measure, resulting in `r nrow(coded_data_replications)` measures in both `r sum(coded_data_replications$appearance == 1)` replications protocols and `r sum(coded_data_original$appearance == 1)` original articles[^1]. Of these `r nrow(coded_data_replications)` measures `r sum(coded_data_replications$mod_check == "True")` were modified from the original to the replication[^2]. In the replications, the data of responses on the measures was further nested in several labs per replication. The combined sample size of all labs in the replications was on average `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N), 0)` which was approximately `r round(mean(coded_data_replications[coded_data_replications$appearance == 1]$N) / mean(coded_data_original_shortened[coded_data_original_shortened$appearance == 1 & !is.na(coded_data_original_shortened$N),]$N), 0)` times larger than the average in original studies, which were conducted in single labs.

@@

[^2]: For 7 measures the number of items were modified from the original article to the replication. To check whether or not this had a confounding impact on our results, we re-ran the analyses testing the hypotheses excluding data from these studies. We found that removing these measures' data had minimal impact on the overall results. Therefore, the results presented below were based on data from all the measures.

@@

We used logistic regression to test the association between the QMP ratio in replication protocols and replication success. In line with Hypothesis 5, results showed that successful replications were associated with fewer QMPs compared to unsuccessful replications (`r H5_test_results_REV_with_OR`). However, we did not find the association with the initial protocol in neither the single-level (`r H5_test_results_with_OR`) nor the multilevel model (`r random_intercept_h5$full_result$QMP`)[^3].

[^3]: As of writing this article the *betareg* package does not allow for estimation of multilevel models. As an approximation, Gaussian random-intercept multilevel models were implemented using the *lmer* function from the *lme4* package [@R-lme4]. The outcome QMP ratio variable was transformed using the logit link function (the default link function in the *betareg* package) to fit the Gaussian model.
